---
title: "Rough Plan"
author: "Rose Campos, Jessenia Contreras"
date: "2024-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Have you ever seen a film, and thought to yourself "Oh my god! This movie is a masterpiece!" Only to look it up and see a 2.4 IMB rating?
Through this report, we take a data set of fifty beloved 'popular' films containing a quantitative measure of level of enjoyment, appreciation, and deemed classical-ness to create a comprehensive analysis that takes into account the film's genre and the demographic of viewers. 
The data we used was gathered from a sample pool of 282 participants of which only 69 where male. The participant pool had an age range of 19 to 37 with the median age range being 22.25. The ethnicity distribution was 39% was Caucasian, 31.5% was Asian, ~13.5% was Hispanic, ~2% was African American, and ~12% Unknown. The remaining percentage is filled by Pacific Islanders and other ethnicity. This data was collected by attendees of the University of Texas at Austin in 2017 for a *Journal of Media Psychology* publication. The goal of the original source was to determine how enjoyment and appreciation could impact viewers aggregate appraisals. The data used is available for download and review at [Data.World](https://data.world/robertjoellewis/enjoyment-versus-appreciation-ratings-of-50-popular-films).

## Data Preparation INSTRUCTIONS

- Data import and cleaning steps are explained in the text and follow a logical process. Tell me why you’re doing what you’re doing.
- Once clean, show me the final data set in the most condensed form possible. (Do NOT print out a data frame with 200+ rows)
- Provide a summary of the variables you’re interested in. Don’t just do str() or summary(), but provide me something like an explanation
with a table or a nice summary paragraph

```{r}
#Packages loading to use
library(tidyverse) ##Loaded for dplyr and to 'clean' data
library(ggplot2) ##Loaded for plotting
library(dplyr) ##Loaded for computer issues

##Read in data and save it to variable raw_data
raw_data <- read.csv(file = "popular_film_data.csv")
glimpse (raw_data)

```
## Data Analysis INSTRUCTIONS
- Uncover new information in the data that isn’t immediately apparent (such as: don’t just plot the data as is, but filter or group the data in
different ways, create new variables, or join different data frames together to get new summaries)
- Provide your findings in plots or tables. Display findings in different ways.
- Graphs all have purpose and help tell your story. Make sure you have a graph that illustrates your primary point and that they are all
appropriately formatted (plot and axis titles, legends if needed, appropriate plot types used)
- Use tables effectively to perform comparisons, highlighting important features.
- Your analysis should be thoroughly, yet concisely, explained. Make sure your insights and discoveries are highlighted, and easy to see and
understand

## Questions
- Which movies were top rated in appreciation / enjoyment?
- What factors relate to the appreciation / enjoyment rated?
- Which genre have the highest appreciation rating? 
- Which genre have the highest enjoyment rating? 
- Does the budget of the movie affect the rating?
- Does gender have an impact on how the movie was rated ?
