---
title: "Films"
author: "Rose Campos, Jessenia Contreras"
date: "2024-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

Have you ever seen a film, and thought to yourself "Oh my god! This movie is a masterpiece!" Only to look it up and see a 2.4 IMB rating?
Through this report, we take a data set of fifty beloved 'popular' films containing a quantitative measure of level of enjoyment, appreciation, and deemed classical-ness to create a comprehensive analysis that takes into account the film's genre and the demographic of viewers. 
The data we used was gathered from a sample pool of 282 participants of which only 69 where male. The participant pool had an age range of 19 to 37 with the median age range being 22.25. The ethnicity distribution was 39% was Caucasian, 31.5% was Asian, ~13.5% was Hispanic, ~2% was African American, and ~12% Unknown. The remaining percentage is filled by Pacific Islanders and other ethnicity. This data was collected by attendees of the University of Texas at Austin in 2017 for a Journal of Media Psychology publication. The goal of the original source was to determine how enjoyment and appreciation could impact viewers aggregate appraisals. The data used is available for download and review at [Data.World](https://data.world/robertjoellewis/enjoyment-versus-appreciation-ratings-of-50-popular-films).

## Data Preparation

Below, we load in the packages we'll be using to analyse our data.  

```{r message=FALSE, warning=FALSE}
#Packages loading to use
library(tidyverse) ##Loaded for dplyr and to 'clean' data
library(ggplot2) ##Loaded for plotting
library(dplyr) ##Loaded for computer issues
library(gridExtra) #Loaded to arrange plots
library(yaml)
library(patchwork)
library(reshape2)

```

Now, we'll read in the data from its .CSV file into our project and save it to the variable **raw_data**. 

```{r}
##Read in data and save it to variable raw_data
raw_data <- read.csv(file = "popular_film_data.csv")
glimpse (raw_data)
```

## Cleaning and Mutating Data

Some of the data contained in the the variables *InflatedBudget*, *InflatedGross*, and *TotalGross* have symbols such as "$" and  ",". These symbols cause the the information in them to be read as characters rather than as integers. We use gsub to remove these symbols.
```{r}
#To remove "$" and "," from InflatedBudget
raw_data$InflatedBudget <-  gsub("\\$","", raw_data$InflatedBudget) 
raw_data$InflatedBudget <-  as.numeric(gsub(",","", raw_data$InflatedBudget))

#To remove "$" and "," from InflatedGross
raw_data$InflatedGross <-  gsub("\\$","", raw_data$InflatedGross) 
raw_data$InflatedGross <-  as.numeric(gsub(",","", raw_data$InflatedGross))

#To remove "$" and "," from TotalGross
raw_data$TotalGross <-  gsub("\\$","", raw_data$TotalGross) 
raw_data$TotalGross <-  as.numeric(gsub(",","", raw_data$TotalGross))

#To View our now changed data. 
glimpse (raw_data)
```
Now, we also see that our data has a *Proportion_male* column. Let's mutate that so we can also see the female ratio and store it in the variable *Proportion_female*.
```{r}
#Mutating for new column stored in Proportion_female
raw_data <- raw_data |> mutate (Proportion_female = (1 - Proportion_male))

#To view our data with the new variable.
glimpse(raw_data)
```

## Data Analysis 

We'll start by learning about our data has. What is the year range of it? How many films make up our data? 
```{r}
#What is the release year range of the films in our dataset?
range(raw_data$Year)

#How many entries make up our dataset?
quantity_films <- nrow(raw_data)
quantity_films
```
We wanted to learn more about the films. First we are looking into how many films of each genre there are? 
```{r}
genre_total <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(sumG = sum(Comedy == 1))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(sumG = sum(Drama == 1))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(sumG = sum(Western == 1))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(sumG = sum(Action == 1))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(sumG = sum(Biography == 1))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(sumG = sum(History == 1))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(sumG = sum(Adventure == 1))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(sumG = sum(Fantasy == 1))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(sumG = sum(Mystery == 1))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(sumG = sum(SciFi == 1))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(sumG = sum(Romance == 1))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(sumG = sum(Thriller == 1))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(sumG = sum(Crime == 1))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(sumG = sum(War == 1))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(sumG = sum(Family == 1))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(sumG = sum(Animation == 1))))%>% arrange(desc(sumG))

genre_total
```

To make this information more visual, we'll plot it below.
```{r}
Genre_Count_Plot <- ggplot(genre_total) + geom_bar(mapping = aes(genre, sumG, fill = genre), stat = "identity", position = "dodge", show.legend = FALSE) + labs(x = 'Genres', y = 'Genre Count', title = 'Genre Distribution in Dataset') + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5))
Genre_Count_Plot
```
Clearly, most of the entries in our dataset are of adventure films, and drama films. There isn't an even distribution of the genres in the dataset - this might skewer the remaining of our analysis towards this those genres. Another thing to keep in mind is that each film can have more than one genre. 

Now, we'll look at the year distribution of our film entries. Does the data contain multiple films per year? Is so, what is the count for each year? 
```{r}
 raw_data|>group_by(Year) |> summarise(Movie_Count = n()) |> arrange(desc(Movie_Count))

```
The above is arranged by to be descending by amount of movies present of each year but it is difficult to see this overall. To give visibility to this distribution we create a plot based on the above. First, we save it to a variable. 

```{r}
#Storing the code to the "count_movieby_year" variable. 

count_movieby_year <-  raw_data|>group_by(Year) |> summarise(Movie_Count = n()) |> arrange(desc(Movie_Count))
ggplot(count_movieby_year, aes(x = Year, y = Movie_Count)) + geom_col(fill = "deeppink", color = "black") + labs(x = 'Year', y = 'Film Count', title = 'Film Release Distribution by Year in Dataset') + theme(plot.title = element_text(hjust = 0.5))

```

Notice the distribution of the films in the data. Out of 50 films, only 11 are pre-1990's while the remaining majority are from the early 1990's to the late 2010's. Keep in mind that this uneven distribution of films might impact the conclusions drawn from the data. 

Next, we wanted to find the average budget for each year. We want to see if the year had an impact on the budget. 
```{r echo=TRUE, message=FALSE, warning=FALSE}
Avg_Budget_by_Year <- raw_data |> group_by(Year)|> summarise(InflatedBudget) |> ggplot(aes(Year,InflatedBudget)) +geom_point(size = 2.2, color = "darkmagenta") + geom_smooth(color = "darkorchid4")+labs(x = 'Year', y = 'USD', title = 'Film Budgets by Year') + theme(plot.title = element_text(hjust = 0.5))

Avg_Budget_by_Year
```

From the graph we can see there is a trend. The graphs tell us that the closer we get to the present the budget increases for films. There is a rapid increase in budgets from the year 1990's to the year 2010's.

Now we want to see, if what the relation is between a films budget and gross income. First we focus on the plotting the *InflatedGross* income. 
```{r echo=TRUE, message=FALSE, warning=FALSE}
Avg_Grossing_by_Year <- raw_data |> group_by(Year) |> summarise(InflatedGross) |> ggplot(aes(Year,InflatedGross)) +geom_point(size = 2.2, color = "darkgreen") + geom_smooth(color = "darkslategray") + labs(x = 'Year', y = 'USD', title = 'Film Inflated Grossins per Year') + theme(plot.title = element_text(hjust = 0.5))

Avg_Grossing_by_Year

```

It's a little hard to compare the *InflatedGross* income and the *InflatedBudget* in two graphs so lets display this information together so we can analyse it. 

```{r echo=TRUE, message=FALSE, warning=FALSE}
#raw_data |> group_by(Year)|> ggplot(aes(Year,InflatedGross, InflatedBudget, color = )) +geom_point() + geom_smooth(method = 'loess', formula = 'y~x')

raw_data |> group_by(Year) |> ggplot(aes(x=Year))+geom_point(aes(y=InflatedBudget),color = "darkmagenta") + geom_point(aes(y=InflatedGross), color = "darkgreen") + geom_smooth(aes(y=InflatedBudget), color = "darkorchid4") +labs(x = "Year", y = "USD") + geom_smooth(aes(y=InflatedGross), color = "darkslategray") + labs(x = 'Year', y = 'USD', title = 'Inflated Budget vs Inflated Grossins per Year') + theme(plot.title = element_text(hjust = 0.5))

```

The graph is not wrong, but both variables have a different y-scale, with the difference being of millions of dollars. Due to this difference we can't see how the budget changes with the years. To overcome this, we'll stack the plots. 
```{r echo=TRUE, message=FALSE, warning=FALSE}
plot_1 <- (Avg_Budget_by_Year / Avg_Grossing_by_Year)
plot_1
```

Since the graphs are now separate from each other, we can see the data in more details. We can tell the difference in each category more clearly. 

We can tell from this graph that companies put a lot of money in to production of the movie but they don't make that money back. 
Now let get a closer look on which years actually made the most money.

First we wanted to see which year had the highest budget.

```{r}
raw_data |> slice_max(InflatedBudget, n = 10) |> select(FilmName, Year, InflatedGross)
```

Then we wanted to look for the year the had the highest Gross.

```{r}
raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, Year,InflatedGross)
```

From this data we can confirm that the movies with the highest budget doesn't mean that it will make the highest gross.

We know the answers to these questions for individual film entries - now we'll answer them for the genre category. 
Here we are looking at the budget,gross, female proportions and the male proportions.

```{r echo=TRUE, message=FALSE, warning=FALSE}
#We'll arrange the code to output what we need to see. 
genreGrossBudget <- (rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meangross = mean(InflatedGross), meanBudget = mean(InflatedBudget), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
     cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget), Malegross = ((mean(Proportion_male))*meangross), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))), 
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
        cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Thriller", raw_data %>% filter(Drama == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross)))) %>% arrange(desc(meanBudget)))
genreGrossBudget

```


#Over all, what genre cost more to produce on average? How much did that category produce in grossing? 

```{r}
genreGrossBudget |> slice(which(meanBudget ==max(meanBudget) | meanBudget == min(meanBudget))) |> distinct()
```
    
We want to see all of that information in a way that is visually apealing and easy to understand. We'll create a graphs for each of these and arrange them side-by-side.  

```{r}
meanBudget_Genre <- (ggplot(genreGrossBudget) + geom_bar(mapping = aes(genre, meanBudget, fill = genre), stat = "identity") + labs(x = 'Genre', y = 'USD', title = 'Mean Budget per Genre') + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5)))

meanGross_Genre <- ggplot(genreGrossBudget) + geom_bar(mapping = aes(genre, meangross, fill = genre), stat = "identity", show.legend = FALSE) + labs(x = 'Genre', y = 'USD', title = 'Mean Grossings per Genre') + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5))

grid.arrange(meanBudget_Genre, meanGross_Genre, nrow = 1)
```

Now we'll plot each genre, and their grossing by sex. We visually want to see if there was a distinction between sex by genres. Since most of our participants was mostly females. 
```{r Plotting sex proportion w/  meangross}
#genreGrossBudget <- genreGrossBudget |> mutate ( Gross_Female = (as.numeric(genreGrossBudget$meangross) * as.numeric(raw_data$Proportion_female)))

genreGrossBudget |> pivot_longer(cols = ends_with("alegross"), names_to = "Sex", values_to = "proportion") |> ggplot() + geom_col(aes(x = genre, y = proportion, fill = Sex)) + labs(x = 'Genre', y = 'USD', title = 'Mean Grossings by Sex per Genre') + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_discrete(labels = c("Female Grossing", "Male Grossing"))
```

Enjoyment is classified as how much the participants enjoy the film. Below, we'll plot the rated enjoyment by genre. Then we look for the genre that was most/least enjoyable by the participants.
```{r}

genre_enj <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meanenj = mean(Enjoyment))))%>% arrange(desc(meanenj))

genre_enj |> slice(which(meanenj ==max(meanenj) | meanenj == min(meanenj))) |> distinct()

```

Appreciation is classified as how much the participants appreciate the films. Below, we'll plot appreciation by genre.  Then we look for the genre that was most/least appreciate by the participants.
```{r}
genre_app <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meanapp = mean(Appreciation))))%>% arrange(desc(meanapp))

genre_app |> slice(which(meanapp ==max(meanapp) | meanapp == min(meanapp))) |> distinct()
```
We'll now visually compare enjoyment and appreciation by genre.

```{r}
combined_df <- merge(genre_app, genre_enj, by="genre", all=TRUE)
combined_df.long<-melt(combined_df)

ggplot(combined_df.long,aes(genre,value, fill=variable))+
     geom_bar(stat="identity",position="dodge")+ theme(axis.text.x = element_text(angle = 60, hjust = 1))+facet_wrap(~genre)


```


Lastly we are comparing the top appreciation/enjoyment to the top gross.

```{r}
raw_data |> slice_max(Appreciation, n = 10)|> select(FilmName,Appreciation, Enjoyment)

raw_data |> slice_max(Enjoyment, n = 10) |> select(FilmName, Enjoyment, Appreciation)

raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, InflatedGross, Appreciation, Enjoyment)
```

We can see that the top appreciation have different films compare to the top enjoyment. Now we want to see if any of the films from our finding will differentiate from the top gross category. 

```{r}
raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, InflatedGross, Appreciation, Enjoyment)
```
The top gross film was Titanic which place 5th in the appreciation top 10 but not in enjoyment top 10. In conclusion gross doesn't mean that it will be the best film. It just mean that it made the most money. Just watch the films that you enjoy and appreciate. Its all opinions anyways. 

