---
title: "Rough Plan"
author: "Rose Campos, Jessenia Contreras"
date: "2024-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction
Provide an informative introduction that explains the problem statement you’re answering. Why should I be interested in reading your
report?
- Provide a short explanation of how you’re addressing this problem statement, what data are you using, what methods are you using?
- Discuss your approach and analytic techniques and why it will address this problem.
- Explain how your analysis will help the reader of the analysis

Have you ever seen a film, and thought to yourself "Oh my god! This movie is a masterpiece!" Only to look it up and see a 2.4 IMB rating?
Through this report, we take a data set of fifty beloved 'popular' films containing a quantitative measure of level of enjoyment, appreciation, and deemed classical-ness to create a comprehensive analysis that takes into account the film's genre and the demographic of viewers. 
The data we used was gathered from a sample pool of 282 participants of which only 69 where male. The participant pool had an age range of 19 to 37 with the median age range being 22.25. The ethnicity distribution was 39% was Caucasian, 31.5% was Asian, ~13.5% was Hispanic, ~2% was African American, and ~12% Unknown.


##Questions
-which movies were top rated in appreciation / enjoyment?
-Does genre 

##Package Loaded
- Explain why each package is loaded. 
```{r cars}
summary(cars)
```

##Data Preparation

Source of the data is cited and hyperlinked, if possible.
- Source data is thoroughly explained (who collected it, why was it collected, when was it collected, think about any peculiarities of the data
such as missing values or quirks of collection.)
- Data import and cleaning steps are explained in the text and follow a logical process. Tell me why you’re doing what you’re doing.
- Once clean, show me the final data set in the most condensed form possible. (Do NOT print out a data frame with 200+ rows)
- Provide a summary of the variables you’re interested in. Don’t just do str() or summary(), but provide me something like an explanation
with a table or a nice summary paragraph
```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

##Data Analysis
- Uncover new information in the data that isn’t immediately apparent (such as: don’t just plot the data as is, but filter or group the data in
different ways, create new variables, or join different data frames together to get new summaries)
- Provide your findings in plots or tables. Display findings in different ways.
- Graphs all have purpose and help tell your story. Make sure you have a graph that illustrates your primary point and that they are all
appropriately formatted (plot and axis titles, legends if needed, appropriate plot types used)
- Use tables effectively to perform comparisons, highlighting important features.
- Your analysis should be thoroughly, yet concisely, explained. Make sure your insights and discoveries are highlighted, and easy to see and
understand
