---
title: 'Films'
author: 'Rose Campos Jessenia Contreras'
date: '2024'
output: powerpoint_presentation: 
reference_doc: Test.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Data Introduction
This data was collected by attendees of the University of Texas at Austin in 2017 for a Journal of Media Psychology publication. The goal of the original source was to determine how enjoyment and appreciation could impact viewers aggregate appraisals. The data used is available for download and review at [Data.World](https://data.world/robertjoellewis/enjoyment-versus-appreciation-ratings-of-50-popular-films).

* Sample pool: 282 
  + Only 69 males 
* Age Distribution: 19 to 37 
  + Median Age: 22.25 
* Ethinicity Distribution: 
  + 39% was Caucasian
  + 31.5% was Asian
  + ~13.5% was Hispanic
  + ~2% was African American
  + ~12% Unknown
  + Remaining % Pacific Islanders and other ethnicities
 

## Data Preparation

Below, we load in the packages we'll be using to analyse our data.  

```{r}
#Packages loading to use
library(tidyverse) ##Loaded for dplyr and to 'clean' data
library(ggplot2) ##Loaded for plotting
library(dplyr) ##Loaded for computer issues
library(gridExtra) #Loaded to arrange plots
library(yaml)

##Read in data and save it to variable raw_data
raw_data <- read.csv(file = "popular_film_data.csv")
```

## Cleaning and Mutating Data
Some of the data contained in the the variables *InflatedBudget*, *InflatedGross*, and *TotalGross* have symbols such as "$" and and ",". These symbols cause the the information in them to be read as characters rather then as integers. We use gsub to remove these symbols. Additionally, we mutated a variable called *Proportion_female* so we could store the female ratio of the sample group for that film. 
```{r}
#To remove "$" and "," from InflatedBudget
raw_data$InflatedBudget <-  gsub("\\$","", raw_data$InflatedBudget) 
raw_data$InflatedBudget <-  as.numeric(gsub(",","", raw_data$InflatedBudget))

#To remove "$" and "," from InflatedGross
raw_data$InflatedGross <-  gsub("\\$","", raw_data$InflatedGross) 
raw_data$InflatedGross <-  as.numeric(gsub(",","", raw_data$InflatedGross))

#To remove "$" and "," from TotalGross
raw_data$TotalGross <-  gsub("\\$","", raw_data$TotalGross) 
raw_data$TotalGross <-  as.numeric(gsub(",","", raw_data$TotalGross))

#Mutating for new column stored in Proportion_female
raw_data <- raw_data |> mutate (Proportion_female = (1 - Proportion_male))
```

```{r include=FALSE}
#For transparencys sake, its also important to note how many films under each genre make up the dataset.
genre_total <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(sumG = sum(Comedy == 1))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(sumG = sum(Drama == 1))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(sumG = sum(Western == 1))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(sumG = sum(Action == 1))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(sumG = sum(Biography == 1))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(sumG = sum(History == 1))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(sumG = sum(Adventure == 1))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(sumG = sum(Fantasy == 1))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(sumG = sum(Mystery == 1))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(sumG = sum(SciFi == 1))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(sumG = sum(Romance == 1))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(sumG = sum(Thriller == 1))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(sumG = sum(Crime == 1))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(sumG = sum(War == 1))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(sumG = sum(Family == 1))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(sumG = sum(Animation == 1))))%>% arrange(desc(sumG))

genre_total
#the end of numbers of genre

#ggplot(genre_total) + geom_histogram(mapping = aes(x = (genre_total$stat = "count"), stat = "identity"))+ geom_histogram(bins = 15)
#ggplot(genre_total, aes(x = (genre_total$stat = "count"), stat = "identity") + geom_histogram(bins = 15))
Genre_Count_Plot <- ggplot(genre_total) + geom_bar(mapping = aes(genre, sumG, fill = genre), stat = "identity", position = "dodge") + labs(x = 'Genres', y = 'Genre Count', title = 'Genre Distribution in Dataset') + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5))



```

## Glimpse(raw_data)
```{r}
#To view our data with the new variable.
glimpse(raw_data)
```

## Data Analysis 
```{r echo=FALSE}

max_year <- max(raw_data$Year)
min_year <- min(raw_data$Year)
Year_range <- range(raw_data$Year)
cat("The year range of our data is ", min_year, "to ", max_year, ".")
quantity_films <- nrow(raw_data)

cat("\nOur dataset is made up of ", quantity_films, " films.")
Genre_Count_Plot
```

## Film Count by Year 
```{r echo=FALSE}
count_movieby_year <-  raw_data|>group_by(Year) |> summarise(Movie_Count = n()) |> arrange(desc(Movie_Count))
ggplot(count_movieby_year, aes(x = Year, y = Movie_Count)) + geom_col(fill = "deeppink", color = "black") + labs(x = 'Year', y = 'Film Count', title = 'Film Release Distribution by Year in Dataset') + theme(plot.title = element_text(hjust = 0.5))
```

```{r include=FALSE}
Avg_Budget_by_Year <- raw_data |> group_by(Year)|> summarise(InflatedBudget) |> ggplot(aes(Year,InflatedBudget)) +geom_point(size = 2.2, color = "darkmagenta") + geom_smooth(color = "darkorchid4")+labs(x = 'Year', y = 'Inflated Budget', title = 'Film Budgets by Year') + theme(plot.title = element_text(hjust = 0.5))
```

## Inflated Budget by Year
```{r echo=FALSE, message=FALSE, warning=FALSE}
Avg_Budget_by_Year
```

```{r include=FALSE}
Avg_Grossing_by_Year <- raw_data |> group_by(Year) |> summarise(InflatedGross) |> ggplot(aes(Year,InflatedGross)) +geom_point(size = 2.2, color = "darkgreen") + geom_smooth(color = "darkslategray") + labs(x = 'Year', y = 'USD', title = 'Film Inflated Grossins per Year') + theme(plot.title = element_text(hjust = 0.5))

```
## Inflated Grossing v. Year
```{r echo=FALSE, message=FALSE, warning=FALSE}
Avg_Grossing_by_Year
```

## InflatedGross v. InflatedBudget by Year
```{r echo=FALSE, message=FALSE, warning=FALSE}
##It's a little hard to compare the *InflatedGross* income and the *InflatedBudget* in two graphs so lets display this information together so we can analyse it. 
#raw_data |> group_by(Year)|> ggplot(aes(Year,InflatedGross, InflatedBudget, color = )) +geom_point() + geom_smooth(method = 'loess', formula = 'y~x')
raw_data |> group_by(Year) |> ggplot(aes(x=Year))+geom_point(aes(y=InflatedBudget),color = "darkmagenta") + geom_point(aes(y=InflatedGross), color = "darkgreen") + geom_smooth(aes(y=InflatedBudget), color = "darkorchid4") + geom_smooth(aes(y=InflatedGross), color = "darkslategray") + labs(x = 'Year', y = 'USD', title = 'Inflated Budget vs Inflated Grossins per Year') + theme(plot.title = element_text(hjust = 0.5))
```


## InflatedGross v. InflatedBudget by Year (Side-By-Side)


```{r include=FALSE}
raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, Year, InflatedGross)

```
# Genres
```{r message=FALSE, include=FALSE}
#Is there a specific genre that costs more to produce? First, we'll see what the most and least expensive films to produce where.
raw_data |> slice_max(InflatedBudget, n = 1) |> select(FilmName, InflatedGross)
raw_data |> slice_min(InflatedBudget, n = 1) |> select(FilmName, InflatedGross)

```

```{r message=FALSE, include=FALSE}
#And what films made the most and least grossing? What genres were these films?
raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, InflatedGross)
#still need the genre
```

```{r message=FALSE, include=FALSE}
#We'll arrange the code to output what we need to see. 
genreGrossBudget <- (rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meangross = mean(InflatedGross), meanBudget = mean(InflatedBudget), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
     cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget), Malegross = ((mean(Proportion_male))*meangross), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))), 
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
        cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Thriller", raw_data %>% filter(Drama == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross)))) %>% arrange(desc(meanBudget)))
genreGrossBudget

```



```{r include=FALSE}
#Over all, what genre cost more to produce on average? How much did that category produce in grossings?

#Over all, what genre cost more to produce on average? How much did that category produce in grossing? 
genreGrossBudget |> slice(which(meanBudget ==max(meanBudget) | meanBudget == min(meanBudget))) |> distinct()

```
    

## Genres:Inflated Grossing v. Inflated Budget
```{r echo=FALSE}
meanBudget_Genre <- ggplot(genreGrossBudget) + geom_bar(mapping = aes(genre, meanBudget, fill = genre), stat = "identity") + labs(x = 'Genre', y = 'USD', title = 'Mean Budget per Genre') + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5))

meanGross_Genre <- ggplot(genreGrossBudget) + geom_bar(mapping = aes(genre, meangross, fill = genre), stat = "identity", show.legend = FALSE) + labs(x = 'Genre', y = 'USD', title = 'Mean Grossings per Genre') + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5))

grid.arrange(meanBudget_Genre, meanGross_Genre, nrow = 1)

```

## Female v. Male for Genre Mean Inflated Grossing
```{r echo=FALSE}
genreGrossBudget |> pivot_longer(cols = ends_with("alegross"), names_to = "Sex", values_to = "proportion") |> ggplot() + geom_col(aes(x = genre, y = proportion, fill = Sex)) + labs(x = 'Genre', y = 'USD', title = 'Mean Grossings by Sex per Genre') + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_discrete(labels = c("Female Grossing", "Male Grossing"))
```



```{r include=FALSE}
#genre enjoyment
genre_enj <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meanenj = mean(Enjoyment))))%>% arrange(desc(meanenj))

genre_enj |> slice(which(meanenj ==max(meanenj) | meanenj == min(meanenj))) |> distinct()

```

```{r include=FALSE}
#genre appreaction
genre_app <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meanapp = mean(Appreciation))))%>% arrange(desc(meanapp))

genre_app |> slice(which(meanapp ==max(meanapp) | meanapp == min(meanapp))) |> distinct()
```


## Let see what movie is actually the best. 
```{r eval=FALSE, include=FALSE}
raw_data |> slice_max(Appreciation, n = 10)|> select(FilmName,Appreciation, Enjoyment)

raw_data |> slice_max(Enjoyment, n = 10) |> select(FilmName, Enjoyment, Appreciation)

raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, InflatedGross, Appreciation, Enjoyment)
```


## Questions

- Which movies were top rated in appreciation / enjoyment?

- Which genre have the highest appreciation rating? 
- Which genre have the highest enjoyment rating? 
which genre cost more to produce? dome
which genre has the highest income? Which sex contributes more to that income. Mutate each film to multiply ratio by income. Then Summarize by genre = true. Repeat for male so you can see both contributions. 
**We still have the classical-ness and popularity to mess around with. 

- Gender and how it affects budget. (Which gender contributes more to the gross of each genre- after budge/gross | pink blue)
apreciation per genre
enjoyment and genre


