---
title: "Films"
author: "Rose Campos, Jessenia Contreras"
date: "2024-04-04"
output: powerpoint_presentation
#reference_doc: Films_raw_theme.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Data Introduction
This data was collected by attendees of the University of Texas at Austin in 2017 for a Journal of Media Psychology publication. The goal of the original source was to determine how enjoyment and appreciation could impact viewers aggregate appraisals. The data used is available for download and review at [Data.World](https://data.world/robertjoellewis/enjoyment-versus-appreciation-ratings-of-50-popular-films).

* Sample pool: 282 
  + Only 69 males 
* Age Distribution: 19 to 37 
  + Median Age: 22.25 
* Ethinicity Distribution: 
  + 39% was Caucasian
  + 31.5% was Asian
  + ~13.5% was Hispanic
  + ~2% was African American
  + ~12% Unknown
  + Remaining % Pacific Islanders and other ethnicities
 

## Data Preparation

Below, we load in the packages we'll be using to analyse our data.  

```{r}
#Packages loading to use
library(tidyverse) ##Loaded for dplyr and to 'clean' data
library(ggplot2) ##Loaded for plotting
library(dplyr) ##Loaded for computer issues

##Read in data and save it to variable raw_data
raw_data <- read.csv(file = "popular_film_data.csv")
```

## Cleaning and Mutating Data
Some of the data contained in the the variables *InflatedBudget*, *InflatedGross*, and *TotalGross* have symbols such as "$" and and ",". These symbols cause the the information in them to be read as characters rather then as integers. We use gsub to remove these symbols. Additionally, we mutated a variable called *Proportion_female* so we could store the female ratio of the sample group for that film. 
```{r}
#To remove "$" and "," from InflatedBudget
raw_data$InflatedBudget <-  gsub("\\$","", raw_data$InflatedBudget) 
raw_data$InflatedBudget <-  as.numeric(gsub(",","", raw_data$InflatedBudget))

#To remove "$" and "," from InflatedGross
raw_data$InflatedGross <-  gsub("\\$","", raw_data$InflatedGross) 
raw_data$InflatedGross <-  as.numeric(gsub(",","", raw_data$InflatedGross))

#To remove "$" and "," from TotalGross
raw_data$TotalGross <-  gsub("\\$","", raw_data$TotalGross) 
raw_data$TotalGross <-  as.numeric(gsub(",","", raw_data$TotalGross))

#Mutating for new column stored in Proportion_female
raw_data <- raw_data |> mutate (Proportion_female = (1 - Proportion_male))
```

```{r include=FALSE}
#For transparencys sake, its also important to note how many films under each genre make up the dataset.
genre_total <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(sumG = sum(Comedy == 1))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(sumG = sum(Drama == 1))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(sumG = sum(Western == 1))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(sumG = sum(Action == 1))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(sumG = sum(Biography == 1))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(sumG = sum(History == 1))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(sumG = sum(Adventure == 1))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(sumG = sum(Fantasy == 1))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(sumG = sum(Mystery == 1))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(sumG = sum(SciFi == 1))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(sumG = sum(Romance == 1))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(sumG = sum(Thriller == 1))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(sumG = sum(Crime == 1))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(sumG = sum(War == 1))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(sumG = sum(Family == 1))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(sumG = sum(Animation == 1))))%>% arrange(desc(sumG))

genre_total
#the end of numbers of genre

#ggplot(genre_total) + geom_histogram(mapping = aes(x = (genre_total$stat = "count"), stat = "identity"))+ geom_histogram(bins = 15)
#ggplot(genre_total, aes(x = (genre_total$stat = "count"), stat = "identity") + geom_histogram(bins = 15))
Genre_Count_Plot <- ggplot(genre_total) + geom_bar(mapping = aes(genre, sumG), stat = "identity")


```
## Glimpse(raw_data)
```{r}
#To view our data with the new variable.
glimpse(raw_data)
```

## Data Analysis 

We'll start by learning about our data has. What is the year range of it? How many films make up our data? How many films of each genere are there? 
```{r echo=FALSE}
#What is the release year range of the films in our dataset?
range(raw_data$Year)

#How many films make up our dataset?
print(nrow(raw_data))

#What is the genre distribution of our dataset?
Genre_Count_Plot
```
## Movie by Year 
Does the data contain multiple films per year? Is so, what is the count for each year?

```{r echo=FALSE}
#Storing the code to the "count_movieby_year" variable.
count_movieby_year <-  raw_data|>group_by(Year) |> summarise(Movie_Count = n()) |> arrange(desc(Movie_Count))
ggplot(count_movieby_year, aes(x = Year, y = Movie_Count)) + geom_col()
```

## Average Budget by Year
```{r echo=FALSE}
raw_data |> group_by(Year)|> summarise(InflatedBudget) |> ggplot(aes(Year,InflatedBudget)) +geom_point() + geom_smooth()
```


## Inflated Grossing v. Year
```{r}
raw_data |> group_by(Year) |> summarise(InflatedGross) |> ggplot(aes(Year,InflatedGross)) +geom_point() + geom_smooth()

```

## InflatedGross v. InflatedBudget by Year
It's a little hard to compare the *InflatedGross* income and the *InflatedBudget* in two graphs so lets display this information together so we can analyse it. 
```{r}
#raw_data |> group_by(Year)|> ggplot(aes(Year,InflatedGross, InflatedBudget, color = )) +geom_point() + geom_smooth(method = 'loess', formula = 'y~x')

raw_data |> group_by(Year) |> ggplot(aes(x=Year))+geom_point(aes(y=InflatedBudget),color = "red") + geom_point(aes(y=InflatedGross), color = "blue") + geom_smooth(aes(y=InflatedBudget), color = "red") + geom_smooth(aes(y=InflatedGross), color = "blue")


```

## InflatedGross v. InflatedBudget by Year (Side-By-Side)


```{r include=FALSE}
#we can tell from this graph that companies put a lot of money in to production of the movie but they don"t make that money back. 
#Now let get a closer look on which years actually made the most money. This data will be use later to compare which movie is the best. 

raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, Year, InflatedGross)
```



## Genres

Is there a specific genre that costs more to produce? First, we'll see what the most and least expensive films to produce where.

```{r}
raw_data |> slice_max(InflatedBudget, n = 1) |> select(FilmName, InflatedGross)
raw_data |> slice_min(InflatedBudget, n = 1) |> select(FilmName, InflatedGross)

```


And what films made the most and least grossing? What genres where these films?

```{r}
raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, InflatedGross)
#still need the genre
```
We know the answers to these questions for indivudual film entries - now we'll answer them for the genre category. 

```{r}
#We'll arrange the code to output what we need to see. 
genreGrossBudget <- (rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meangross = mean(InflatedGross), meanBudget = mean(InflatedBudget), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
      cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
     cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget), Malegross = ((mean(Proportion_male))*meangross), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))), 
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
        cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Thriller", raw_data %>% filter(Drama == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget),  Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meangross = mean(InflatedGross),meanBudget = mean(InflatedBudget), Male_Proportion = Proportion_male, Female_Proportion = Proportion_female, Femalegross = ((mean(Proportion_female))*meangross), Malegross = ((mean(Proportion_male))*meangross)))) %>% arrange(desc(meanBudget)))
genreGrossBudget

```



```{r}
#Over all, what genre cost more to produce on average? How much did that category produce in grossings?

#Over all, what genre cost more to produce on average? How much did that category produce in grossing? 
genreGrossBudget |> slice(which(meanBudget ==max(meanBudget) | meanBudget == min(meanBudget))) |> distinct()

```
    
We want to see all of that information in a way that is visually apealing and easy to understand. We'll create a graph. 

```{r}
ggplot(genreGrossBudget) + geom_bar(mapping = aes(genre, meanBudget), stat = "identity")

#ggplot for meangross
ggplot(genreGrossBudget) + geom_bar(mapping = aes(genre, meangross), stat = "identity")
```
Mutate to add avg malegross and femalegross. 

```{r}
#genreGrossBudget <- genreGrossBudget |> mutate ( Gross_Female = (as.numeric(genreGrossBudget$meangross) * as.numeric(raw_data$Proportion_female)))

genreGrossBudget |> pivot_longer(cols = ends_with("alegross"), names_to = "gender", values_to = "proportion") |> ggplot() + geom_col(aes(x = genre, y = proportion, fill = gender))
```


###T
```{r}
#genre enjoyment
genre_enj <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meanenj = mean(Enjoyment))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meanenj = mean(Enjoyment))))%>% arrange(desc(meanenj))

genre_enj |> slice(which(meanenj ==max(meanenj) | meanenj == min(meanenj))) |> distinct()

```

```{r}
#genre appreaction
genre_app <- rbind(cbind(genre = "Comedy", raw_data %>% filter(Comedy == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Drama", raw_data %>% filter(Drama == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Western", raw_data %>% filter(Western == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Action", raw_data %>% filter(Action == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Biography", raw_data %>% filter(Biography == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "History", raw_data %>% filter(History == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Adventure", raw_data %>% filter(Adventure == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Fantasy", raw_data %>% filter(Fantasy == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Mystery", raw_data %>% filter(Mystery == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "SciFi", raw_data %>% filter(SciFi == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Romance", raw_data %>% filter(Romance == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Thriller", raw_data %>% filter(Thriller == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Crime", raw_data %>% filter(Crime == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "War", raw_data %>% filter(War == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Family", raw_data %>% filter(Family == 1) %>% summarise(meanapp = mean(Appreciation))),
    cbind(genre = "Animation", raw_data %>% filter(Animation == 1) %>% summarise(meanapp = mean(Appreciation))))%>% arrange(desc(meanapp))

genre_app |> slice(which(meanapp ==max(meanapp) | meanapp == min(meanapp))) |> distinct()
```


Let see what movie is actually the best. 
```{r}
raw_data |> slice_max(Appreciation, n = 10)|> select(FilmName,Appreciation, Enjoyment)

raw_data |> slice_max(Enjoyment, n = 10) |> select(FilmName, Enjoyment, Appreciation)

raw_data |> slice_max(InflatedGross, n = 10) |> select(FilmName, InflatedGross, Appreciation, Enjoyment)
```


## Questions

- Which movies were top rated in appreciation / enjoyment?

- Which genre have the highest appreciation rating? 
- Which genre have the highest enjoyment rating? 
which genre cost more to produce? dome
which genre has the highest income? Which sex contributes more to that income. Mutate each film to multiply ratio by income. Then Summarize by genre = true. Repeat for male so you can see both contributions. 
**We still have the classical-ness and popularity to mess around with. 

- Gender and how it affects budget. (Which gender contributes more to the gross of each genre- after budge/gross | pink blue)
apreciation per genre
enjoyment and genre


